
Create an empty app

```{r}
# define the modules
modules <- data.frame(
  "component" = c("select", "select", "transform", "plot", "plot"),
  "long_component" = c("Select data", "Select data", "Transform data", "Plot data", "Plot data"),
  "module" = c("async", "query", "filter", "hist", "scatter"),
  "long_module" = c("Upload your own data", "Query a database to obtain data", "Filter the data",
                    "Plot the data as a histogram", "Plot the data as a scatterplot"),
  "map" = c(TRUE, FALSE, TRUE, FALSE, FALSE),
  "result" = c(FALSE, FALSE, TRUE, TRUE, TRUE),
  "rmd" = c(TRUE, TRUE, TRUE, TRUE, TRUE),
  "save" = c(TRUE, TRUE, TRUE, TRUE, TRUE),
  "download" = c(FALSE, FALSE, TRUE, TRUE, TRUE),
  "async" = c(TRUE, FALSE, FALSE, FALSE, FALSE))

common_objects = c("raster", "histogram", "scatter")

# create the app
shinyscholar::create_template(path = file.path("~", "Documents"), name = "SSdemo",
                             include_map = TRUE, include_table = TRUE, include_code = TRUE,
                             common_objects = common_objects, modules = modules,
                             author = "Simon Smart", install = TRUE)

SSdemo::run_SSdemo()

```

Add some modules from the example app

```{r}
# copy modules from shinyscholar example app
select <- list.files(path = system.file("shiny", "modules", package = "shinyscholar"), pattern = "select_", full.names = TRUE)
plot_hist <- list.files(path = system.file("shiny", "modules", package = "shinyscholar"), pattern = "plot_hist", full.names = TRUE)
plot_scat <- list.files(path = system.file("shiny", "modules", package = "shinyscholar"), pattern = "plot_scat", full.names = TRUE)
load <- list.files(path = system.file("shiny", "modules", package = "shinyscholar"), pattern = "core_load", full.names = TRUE)

for (f in c(select, plot_hist, plot_scat, load)){
  file.copy(f, file.path("~", "Documents", "SSdemo", "inst", "shiny", "modules"), overwrite = TRUE)
}

# copy functions 
functions <- c("select_async", "select_query", "plot_hist", "plot_scatter")

for (f in functions){
  url <- glue::glue("https://raw.githubusercontent.com/simon-smart88/shinyscholar/refs/heads/master/R/{f}_f.R")
  download.file(url, file.path("~", "Documents", "SSdemo", f, "_f.R"))
}

# redocument and install (note we'd normally both of these via Ctrl+Shift+B inside a project in RStudio)
devtools::document(file.path("~", "Documents", "SSdemo"))
devtools::install(file.path("~", "Documents", "SSdemo"))

SSdemo::run_SSdemo()

```

Prototype the new function

```{r}

# load raster from saved common
common <- readRDS("SSdemo-session.rds")

# only need because terra objects are pointers to C++ objects - most objects load normally
raster <- terra::unwrap(common$raster)

upper <- 90
lower <- 30

modified_raster <- terra::clamp(raster, lower = lower, upper = upper, values = FALSE)

```

Create the new function

```{r}

#' @title transform_filter
#' @description Does x
#' @param x x
#' @param logger Stores all notification messages to be displayed in the Log
#'   Window. Insert the logger reactive list here for running in
#'   shiny, otherwise leave the default NULL
#' @return NULL
#' @examples {
#' y <- transform_filter(1)  
#' }
#' @export
transform_filter <- function(x, logger = NULL){
  NULL
}

```

Write unit tests

- raster needs to be a SpatRaster
- lower and upper need to be numeric

- Number of pixels shouldn't change
- Max value = upper
- Min value = lower

```{r}
test_that("Check transform_filter function works as expected", {
  result <- transform_filter()
  expect_true(is.null(result))
})

```

Create the module

```{r}
transform_filter_module_ui <- function(id) {
  ns <- shiny::NS(id)
  tagList(
    # UI

    actionButton(ns("run"), "Run module transform_filter", icon = icon("arrow-turn-down")),
    downloadButton(ns("download"), "Download")


  )
}

transform_filter_module_server <- function(id, common, parent_session, map) {
  moduleServer(id, function(input, output, session) {

  shinyjs::hide("download")

  observeEvent(input$run, {
    # WARNING ####

    # FUNCTION CALL ####

    # LOAD INTO COMMON ####

    # METADATA ####
    # Populate using metadata()

    # TRIGGER
    trigger("transform_filter")

    shinyjs::show("download")

  })

  output$result <- renderText({
    watch("transform_filter")
    # Result
  })

  output$download <- downloadHandler(
    filename = function() {
      "placeholder.ext"
    },
    content = function(file) {
      # Download content
    })

  return(list(
    save = function() {
      # Save any values that should be saved when the current session is saved
      # Populate using save_and_load()
    },
    load = function(state) {
      # Load
      # Populate using save_and_load()
    }
  ))

})
}


transform_filter_module_result <- function(id) {
  ns <- NS(id)

  # Result UI
  verbatimTextOutput(ns("result"))
}

transform_filter_module_map <- function(map, common) {
  # Map logic
}

transform_filter_module_rmd <- function(common) {
  # Variables used in the module's Rmd code
  # Populate using metadata()
}




```

Add metadata and save lines

```{r}
# inside a project save_and_load(".", "transform_filter") would work
shinyscholar::save_and_load(file.path("~", "Documents", "SSdemo"), "transform_filter")
shinyscholar::metadata(file.path("~", "Documents", "SSdemo"), "transform_filter")

```

Module configuration

```{yaml}
component: "transform"
short_name: "Filter"
long_name: "Filter the data"
authors: "Simon Smart"
package: []
```

Add a reproducible chunk
(Copy after running `metadata()`)

```{r}


```

End-to-end tests

```{r}
test_that("{shinytest2} recording: e2e_transform_filter", {
  app <- shinytest2::AppDriver$new(app_dir = system.file("shiny", package = "SSdemo"), name = "e2e_transform_filter")
  app$set_inputs(tabs = "transform")
  app$set_inputs(transformSel = "transform_filter")
  app$click("transform_filter-run")
  common <- app$get_value(export = "common")
  expect_true(is.null(common$scatter))
})

```

